Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 revise/revise.tex
Add comment on 'slowness' (Closes #43)
Add fuel-moderator heating answer to revise.tex

\question It's somehow interesting that ``For some three-dimensional
simulations, the number of elements in the mesh and total number of degrees of
freedom exceed one million and ten million respectively. To handle problems of
this size, we ran Moltres on up to 608 cores.'' Normally problems of few million
degrees of freedom can be handled with few tens of cores. The authors should
discuss more extensively the performances of their code in order to give the
reader the possibility to compare them with those of other tools. In particular,
it is possible that slow performances may derive from trying to achieve a fully
coupled solution (i.e., all the equations in the same matrix), which seems to be
the case in this work. In this sense and to better support the claims of the
paper, it would be important to compare the performances of a segregated and a
fully coupled solver, both in terms of accuracy and computational time. In
addition to helping supporting the claims of the paper, this would represent a
significant contribution to the scientific community, since many of the
currently available tools employ segregated solvers, and since the advantages
and disadvantages of a fully coupled solver are often a subject of discussion.
\begin{solution}
        It is definitely true that for many problems an operator-splitting or
        segregated solution method will be faster and require less
        computational resources. A fully-coupled Newton's method is
        computationally expensive. We could in theory use fewer cores to solve
        our million DOF problems and have the problem run longer. However,
        particularly in our department and with our collaboration with Illinois's
        National Center for Supercomputing Applications, we are encouraged to
        use the computational resources at our disposal, so we elect to run our
        large problems as quickly as possible on Blue Waters. Additionally, the
        developers of PetSc recommend using approximately 20k degrees of freedom
        per process, which is a rule of thumb we generally adhere to.

@@

\question The heat generation in the graphite is calculated as a fraction of
that in the fuel. How exactly is this achieved considering that the two sources
are spatially separated?
\begin{solution}
        <++>
\end{solution}

>>>>

\question It's somehow interesting that ``For some three-dimensional
simulations, the number of elements in the mesh and total number of degrees of
freedom exceed one million and ten million respectively. To handle problems of
this size, we ran Moltres on up to 608 cores.'' Normally problems of few million
degrees of freedom can be handled with few tens of cores. The authors should
discuss more extensively the performances of their code in order to give the
reader the possibility to compare them with those of other tools. In particular,
it is possible that slow performances may derive from trying to achieve a fully
coupled solution (i.e., all the equations in the same matrix), which seems to be
the case in this work. In this sense and to better support the claims of the
paper, it would be important to compare the performances of a segregated and a
fully coupled solver, both in terms of accuracy and computational time. In
addition to helping supporting the claims of the paper, this would represent a
significant contribution to the scientific community, since many of the
currently available tools employ segregated solvers, and since the advantages
and disadvantages of a fully coupled solver are often a subject of discussion.
\begin{solution}
        It is definitely true that for many problems an operator-splitting or
        segregated solution method will be faster and require less
        computational resources. A fully-coupled Newton's method is
        computationally expensive. We could in theory use fewer cores to solve
        our million DOF problems and have the problem run longer. However,
        particularly in our department and with our collaboration with Illinois's
        National Center for Supercomputing Applications, we are encouraged to
        use the computational resources at our disposal, so we elect to run our
        large problems as quickly as possible on Blue Waters. Additionally, the
        developers of PetSc recommend using approximately 20k degrees of freedom
        per process, which is a rule of thumb we generally adhere to. For the 3D
        problem for which we report results (1.16 million DOFs), we are fairly
        pleased with the 2.5 hour solution on 160 cores and do not consider this
        performance as slow, at least in the context of a fully coupled, fully
        implicit solution method.

@@

\question The heat generation in the graphite is calculated as a fraction of
that in the fuel. How exactly is this achieved considering that the two sources
are spatially separated?
\begin{solution}
        A good question. We have a variety of options available, but in this
        work we take a whole-core average of the fuel heat generation and then
        multiply by $\gamma$. For a constant $\gamma$ this results in uniform
        heating with the moderator regions. We have added the following passage
        to clarify this point:

        In this work, $Q_g = \gamma V_{\text{core}}^{-1} \int_{\text{core}}Q_f
        \diff V$, where $\gamma$ is a factor representing heat dissipation by
        gamma and neutron irradiation in the moderator, called the graphite to
        fuel power density ratio. Robertson's \cite{robertson_conceptual_1971}
        original \gls{MSBR} analysis included a calculation of $\gamma$.
        \cite{krepel_dyn3d-msr_2007,zhang_development_2009,cammi_multi-physics_2011}
        all calculated gamma heating through such a factor. We follow
        \cite{cammi_multi-physics_2011} and set $\gamma=0.0144$. Notably, the
        Moltres physics kernel for radiation heating can be calculate the volume
        average fission heat in a variety of means: whole-core and local
        averages are possible. Whole-core averages are employed for simplicity
        and in accordance with prior literature.  Knowledge of fision heat
        rates, however, require knowledge of neutron fluxes, implying a need for
        group constants.
\end{solution}
